\propertitle

### 2019-11-17 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-17T16:12:37+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/paper2_stensola_twomom_distributions10000_prior2.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/paper_riehle_twomom_distributions10000_prior2.pdf}%
\caption{***}
\label{fig:plots_2_4mom}
\end{figure}
% maxent_solutions_different_moments_prior2_6moments.nb
To illustrate how our approach can be applied to studies of sufficient
statistics, \fig~\ref{fig:plots_2_4mom} shows the full-network
distributions, for $N=10\,000$, obtained constraining the first two moments
(equivalent to constraining means and correlations) and the first four
moments. The frequency distribution of the sample is also shown for
comparison. In both data sets the two-moment constraint leads to a
distribution quite different from the four-moment constraint. For the first
data set in particular, one distribution is bimodal, the other unimodal.
This visual difference shows directly -- without the need to calculate
relative entropies, for example -- that the first two moments alone are
\emph{not} informationally sufficient for this specific data set.

@@

The same plot also shows the marginals obtained from applying the method to
a full network with $N=10\,000$ and the same constraints, that is, the
sample marginals of \fig~\ref{fig:plots_2_4mom}. The two-moment
distribution is represented by filled red circles
(\textcolor{myred}{\LARGE$\bm{\bullet}$}), and the four-moment one by
filled blue squares (\textcolor{mypurpleblue}{$\bm{\blacksquare}$}). The
full-network distribution fits the measured frequencies very well if we
only keep four moments.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-17T17:07:11+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/newpaper2_stensola_twomom_distributions10000_priorc.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/newpaper2_riehle_twomom_distributions10000_prior2.pdf}%
\caption{***}
\label{fig:plots_2_4mom}
\end{figure}
% maxent_solutions_different_moments_prior2_6moments.nb
To illustrate how our approach can be applied to studies of sufficient
statistics, \fig~\ref{fig:plots_2_4mom} shows the full-network
distributions, for $N=10\,000$, obtained constraining the first two moments
(equivalent to constraining means and correlations) and the first four
moments. The frequency distribution of the sample is also shown for
comparison. In both data sets the two-moment constraint leads to a
distribution quite different from the four-moment constraint. For the first
data set in particular, one distribution is bimodal, the other unimodal.
This visual difference shows directly -- without the need to calculate
relative entropies, for example -- that the first two moments alone are
\emph{not} informationally sufficient for this specific data set.

@@

The same plot also shows the marginals obtained from applying the method to
a full network with $N=10\,000$ and the same constraints, that is, the
sample marginals of \fig~\ref{fig:plots_2_4mom}. The two-moment
distribution is represented by filled red circles
(\textcolor{myred}{\LARGE$\bm{\bullet}$}), and the four-moment one by
filled blue squares (\textcolor{mypurpleblue}{$\bm{\blacksquare}$}). The
full-network distribution fits the measured frequencies
(\textcolor{black}{$\bm{\triangledown}$}) very well if we constrain only four
moments.
